---
title: "Bycatch Paper"
author: "Natasha Besseling"
date: "2023-06-06"
output:
  word_document: default
  html_document: default
editor_options:
  chunk_output_type: inline
---


```{r message=FALSE, warning=FALSE, include=FALSE}
#load packages

library(janitor)
library(fuzzySim)
library(ggthemes)
library(dendextend)
library(vegan)
library(tidyverse)
library(lubridate)
#library(maptools)
library(maps)
library(mapdata)
library(wesanderson)
library(RColorBrewer)
library(sp)
library(gridExtra)
#library(ggsn)  # north2() scalebar()
library(rworldmap) 
library(ggrepel)
library(plotrix)
library(ggdendro)
library(DBI)
library(RPostgres)
library(here)
library(gt)
```


```{r message=FALSE, warning=FALSE, include=FALSE}
#load functions
## Normalise data
normalise <- function(dat, values, id, join) {
  
  test <- dat %>%
    group_by({{id}}) %>%
    summarise(total = sum({{values}}))
  
  test1 <-  dat %>%
    left_join(test, by = {{join}})
  
  test2 <- test1 %>%
    mutate(norm = {{values}} /total)%>%
    select(-total)
}
## pairwise tests for permanova
pairwise.adonis <- function(x,factors, sim.function = 'vegdist', sim.method = 'bray', p.adjust.m ='bonferroni')
{
  library(vegan)
  
  co = combn(unique(as.character(factors)),2)
  pairs = c()
  F.Model =c()
  R2 = c()
  p.value = c()
  
  
  for(elem in 1:ncol(co)){
    if(sim.function == 'daisy'){
      library(cluster); x1 = daisy(x[factors %in% c(co[1,elem],co[2,elem]),],metric=sim.method)
    } else{x1 = vegdist(x[factors %in% c(co[1,elem],co[2,elem]),],method=sim.method)}
    
    ad = adonis(x1 ~ factors[factors %in% c(co[1,elem],co[2,elem])] );
    pairs = c(pairs,paste(co[1,elem],'vs',co[2,elem]));
    F.Model =c(F.Model,ad$aov.tab[1,4]);
    R2 = c(R2,ad$aov.tab[1,5]);
    p.value = c(p.value,ad$aov.tab[1,6])
  }
  p.adjusted = p.adjust(p.value,method=p.adjust.m)
  sig = c(rep('',length(p.adjusted)))
  sig[p.adjusted <= 0.05] <-'.'
  sig[p.adjusted <= 0.01] <-'*'
  sig[p.adjusted <= 0.001] <-'**'
  sig[p.adjusted <= 0.0001] <-'***'
  
  pairw.res = data.frame(pairs,F.Model,R2,p.value,p.adjusted,sig)
  print("Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
  return(pairw.res)
  
} 

```



```{r include=FALSE}
#load the data
#connect to the sql database

con <- dbConnect(RPostgres::Postgres(),
                 dbname = "masters_paper",
                 port = Sys.getenv("DB_PORT"),
                 user = Sys.getenv("DB_USER"),
                 password = Sys.getenv("DB_PASSWORD"))

drag <- dbReadTable(con, "dit_drag_clean" )
landing <- dbReadTable(con, "dit_landing_clean" )


#close connection to the database
dbDisconnect(con)
```




```{r echo=FALSE, message=FALSE, warning=FALSE}
#calculate the bycatch composition by weight
# total number of species

test <- landing %>%
  distinct(species_code)

#47

##total catch composition

test <- landing%>%
  group_by(species_code)%>%
  summarise(mass = sum(nominal_mass, na.rm = T))%>%
  mutate(proportion = mass/sum(mass))

#hake = 50.1
#sole = 4.1


## Top species

species <- landing %>%
  mutate(nominal_mass= nominal_mass/1000)%>% ##make tons
  group_by(scientific_name, docking_date_yy)%>%
  summarise(nominal_mass = sum(nominal_mass, na.rm = T))%>%  ##get total landed mass per year for each species
  # pivot_wider(names_from = docking_date_yy, values_from = nominal_mass)%>% #pivot to a wider table
  # mutate_all(~replace_na(.,0))%>%
  # pivot_longer(cols = 3:12, names_to = "docking_date_yy", values_to = "nominal_mass")%>%
  group_by(scientific_name)%>%
  summarise(nominal_mass=sum(nominal_mass)/30)


species <- species[order(-species$nominal_mass),]

species <- species %>%
  ungroup() %>% 
  mutate(cumsum = round(cumsum(nominal_mass))) %>%
  mutate(percentage = round(nominal_mass/sum(nominal_mass)*100, digits= 2)) %>% 
  mutate(Percent_of_total = round(cumsum/sum(nominal_mass)*100, digits= 2))%>%
  mutate(nominal_mass= round(nominal_mass)) 
# %>% 
#   filter(scientific_name != "Demersal")


topspp <- species %>%
  filter(Percent_of_total < 99)%>%
  select(scientific_name)

species[1:13,] %>% 
  select(-cumsum) %>% 
  gt() %>% 
  tab_header(title = "Average yearly landed catch composition") %>% 
   cols_label(
    scientific_name = html("**Scientific Name**"),
    nominal_mass = html("**Landed mass (t)**"),
    percentage = html("**Percentage**"),
    Percent_of_total = html("**Cumulative Percentage**"),
    .fn = md) %>% 
  cols_align(align = c("center"),
             columns = c(nominal_mass, percentage, Percent_of_total))
```


Cluster analysis of vessels 

```{r echo=FALSE, message=FALSE, warning=FALSE}

#determine if the vessel is a hake or sole directed vessel
target_code <- drag %>%
  count(vessel_number, target_species_code)%>%
  normalise(n, vessel_number, "vessel_number")%>%
  filter(!norm<0.5)%>%
  mutate(target_code = if_else(norm>0.75 & 
                                 target_species_code == "HAKE", 
                               "Hake",
                               if_else(norm>0.75 & 
                                         target_species_code == "ECSOLE", 
                                       "Sole", "both"))) %>% 
  rownames_to_column() %>% 
  mutate(rowname = as.integer(rowname))



####
#cluster
####

#sum the catch by vessel, and normalise and square root the catch comp per vessel
ves.s <- landing%>%
  right_join(topspp)%>%
  group_by(vessel_number,species_code)%>%
  summarise(nominal_mass = sum(nominal_mass, na.rm = T))%>%
  normalise(nominal_mass, vessel_number, "vessel_number")%>%
  mutate(norm = sqrt(norm))%>%
  ungroup()%>%
  select(vessel_number, norm, species_code)%>%
  pivot_wider(names_from = species_code, values_from = norm)%>%
  mutate_all(~replace_na(.,0))%>%
  ungroup()%>% 
  column_to_rownames(var = "vessel_number") 

write.csv(ves.s, "simp.ves.csv", row.names = F)

#distance matrix
dm <- vegdist(ves.s, method="bray", na.rm = T)

#cluster
cluster<- dm %>%
  hclust(method = "average")

#plot the cluster analysis in a dendrogram (try get the numbers the right way)
x <- cluster%>%
  as.dendrogram()%>% 
  dendextend::set("labels_cex", 0.8)%>%
  dendextend::set("branches_lwd", 2)%>%
  colour_branches(h = 0.13, groupLabels = T,
                  col = "black") 


rowname <- order.dendrogram(x)
  
levels <- as.data.frame(rowname)

test <- levels %>% 
  right_join(target_code) %>% 
  mutate(shape = if_else(target_code == "Hake", 17, 
                         if_else(target_code == "Sole", 15,19)))


x1 <- x %>%
  set("leaves_pch",test$shape ) %>%  # node point type
  set("leaves_cex", 1.5) 
  

plot(x1)
title(ylab = 'Dissimilarity', line = 2.5)
title(xlab = 'Vessels', line = 2)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
#get the cluster groups into the catch comp dataframe
dend_list <- get_subdendrograms(x, 5)
labels <- lapply(dend_list, labels)
grp<- labels %>%
  plyr::ldply( rbind)%>%
  t()%>%
  as_tibble()%>%
  pivot_longer(cols= 1:5,names_to = "grp", values_drop_na = T )%>%
  column_to_rownames(var = "value")

ves.s <- ves.s %>%
  merge(grp, by = "row.names")%>%
  mutate(Row.names = as.numeric(Row.names)) %>%
  left_join(select(target_code, vessel_number, target_code), by = c("Row.names" = "vessel_number"))
# 
# 
# #write.csv(ves.s, "simp.ves.csv", , row.names = F)
# 
# #### MDS
# 
# #distance matrix
# 
# dm <- vegdist(ves.s[2:14], method="bray", na.rm = T)
# 
# #Do MDS
# mds <- metaMDS(dm, 
#                k=3,
#                try=15, trymax=20,
#                autotransform = FALSE,#if it doesn't converge increase k by 1. 
#                trace = F)
# 
# 
# MDS_xy <- data.frame(mds$points, mds$stress)
# 
# 
# ggplot(MDS_xy, aes(MDS1, MDS2, shape = ves.s$target_code)) +
#   geom_point(size = 5) + 
#   ggforce::geom_mark_ellipse(aes(MDS1, MDS2, group = ves.s$grp, label = ves.s$grp))+
#   theme(legend.title = element_text(size = 14, face = "bold"), 
#         legend.text = element_text(size = 12, face = "bold"), 
#         legend.position = "right", 
#         axis.text.x = element_text(face = "bold",colour = "black", size = 12), 
#         axis.text.y = element_text(face = "bold", size = 12, colour = "black"), 
#         axis.title.y = element_text(face = "bold", size = 14, colour = "black"),
#         axis.title.x = element_text(face = "bold", size = 14, colour = "black"),
#         panel.background = element_blank(), 
#         panel.border = element_rect(fill = NA, colour = "black"), 
#         legend.key=element_blank()) + 
#   labs(x = "MDS 1", y = "MDS 2", colour = "Cluster", shape = "Target Species") +
#   scale_colour_brewer(palette = "Paired", aesthetics = "colour")


```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#bar graph
grp1 <- grp %>%
  rownames_to_column(var = "vessel_number")

spp <- topspp %>%
  rownames_to_column(var = "id")%>%
  mutate(id = as.numeric(id))

landing%>%
  mutate(vessel_number = as.character(vessel_number)) %>% 
  right_join(spp)%>%
  left_join(grp1)%>%
  group_by(grp, id, species_code)%>%
  summarise(nominal_mass = sum(nominal_mass, na.rm = T))%>%
  normalise(nominal_mass, grp, "grp")%>%
  mutate(norm = sqrt(norm))%>%
  ggplot(aes(reorder(species_code, id), norm))+
  geom_col( position = "dodge")+
  facet_wrap(~grp)+
  theme(
        axis.text.x = element_text(face = "bold",colour = "black", size = 8, 
                                   angle = 90, vjust = 0.5, hjust=1), 
        axis.text.y = element_text(face = "bold", size = 8, colour = "black"), 
        axis.title.y = element_text( face = "bold", size = 12, colour = "black"),
        axis.title.y.right = element_text( face = "bold", size = 12, colour = "blue"),
        axis.title.x = element_text(face = "bold", size = 12, colour = "black"),
        panel.background = element_blank(), 
        panel.border = element_rect(fill = NA, colour = "black")) +
  labs(x = "Species code", y = "Proportion")
# +
#   scale_fill_brewer(palette = "Paired", aesthetics = "fill")

# legend.title = element_blank(), 
#         legend.position = "none", 
#         legend.key=element_blank()

```

Simper analysis of vessels


```{r echo=FALSE, message=FALSE, warning=FALSE}


simp_ves <- simper(ves.s[2:14],ves.s$grp)

comparisons <- c("V4_V3","V4_V2", "V4_V1", "V3_V2", "V3_V1", "V2_V1")

simper.results <- c()

for(i in 1:length(comparisons)) {
require(tidyverse)
temp <- summary(simp_ves)[as.character(comparisons[i])] %>%
as.data.frame()
colnames(temp) <- gsub(
paste(comparisons[i],".", sep = ""), "", colnames(temp))
temp <- temp %>%
mutate(Comparison = comparisons[i],
Position = row_number()) %>%
  rownames_to_column(var = "Species")
simper.results <- rbind(simper.results, temp)
}

simper.results.con <- simper.results %>%
  filter(p <= 0.05) %>%
  select(Species, average, Comparison) %>% 
  mutate(average = round(average*100, digits = 3)) %>% 
  pivot_wider(names_from = Comparison, values_from = average)

grp1 <- grp %>%
  rownames_to_column(var = "vessel_number")

spp <- topspp %>%
  rownames_to_column(var = "id")%>%
  mutate(id = as.numeric(id))

landing%>%
  mutate(vessel_number = as.character(vessel_number)) %>% 
  right_join(spp)%>%
  left_join(grp1)%>%
  group_by(grp,id,species_code)%>%
  summarise(nominal_mass = round(mean(nominal_mass, na.rm = T), digits = 1)) %>% 
  pivot_wider(names_from = grp, values_from = nominal_mass) %>% 
  left_join(simper.results.con, by = c("species_code" = "Species"))%>% 
  ungroup() %>% 
  select(-id)%>%
  select(1,7:9) %>% 
  gt()

```



cluster analysis of year

```{r echo=FALSE, message=FALSE, warning=FALSE}
####
#cluster
####

test <- landing%>%
  right_join(topspp)%>%
  group_by(docking_date_yy, species_code)%>%
  summarise(nominal_mass = sum(nominal_mass, na.rm = T))%>%
  normalise(nominal_mass, docking_date_yy, "docking_date_yy")%>%
  mutate(norm = sqrt(norm))%>%
  select(docking_date_yy, norm, species_code)%>%
  pivot_wider(names_from = species_code, values_from = norm)%>%
  mutate_all(~replace_na(.,0))%>%
  ungroup()%>%
  column_to_rownames(var = "docking_date_yy")


#distance matrix

dm <- vegdist(test, method="bray", na.rm = T)

#cluster

cluster<- dm %>%
  hclust(method = "average")


x <- cluster%>%
  as.dendrogram(xlab = "Years", ylab = "Dissimilarity")%>% 
  dendextend::set("labels_cex", 0.8)%>%
  dendextend::set("branches_lwd", 2)%>%
  colour_branches(h = 0.1, groupLabels = T,
                  col = "black")
plot(x)
title(ylab = 'Dissimilarity', line = 2.5)
title(xlab = 'Years', line = 2)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}

dend_list <- get_subdendrograms(x, 4)
labels <- lapply(dend_list, labels)
grp<- labels %>%
  plyr::ldply( rbind)%>%
  t()%>%
  as_tibble()%>%
  rename(Y1 = V1,
         Y4 = V2,
         Y3 = V3,
         Y2 = V4)%>%
  pivot_longer(cols= 1:4,names_to = "grp", values_drop_na = T )%>%
  column_to_rownames(var = "value")


year.s <- merge(test, grp, by = "row.names")



#### MDS

#distance matrix

dm <- vegdist(year.s[2:14], method="bray", na.rm = T)

#Do MDS
mds <- metaMDS(dm, 
               k=3,
               try=15, trymax=20,
               autotransform = FALSE,#if it doesn't converge increase k by 1. 
               trace = F)         


MDS_xy <- data.frame(mds$points)

test <- year.s %>%
  mutate(path = "a")

ggplot(MDS_xy, aes(MDS1, MDS2)) + #, colour = test$grp
  geom_path(group= test$path)+
  geom_text(label= test$Row.names, nudge_x = 0.015)+
  #  geom_line(group= test$grp)+
  ggforce::geom_mark_ellipse(aes(MDS1, MDS2, group = test$grp, label = test$grp))+
  geom_point(size = 2) + 
  theme(legend.title = element_text(size = 14, face = "bold"), 
        legend.text = element_text(size = 12, face = "bold"), 
        legend.position = "right", 
        axis.text.x = element_text(face = "bold",colour = "black", size = 12), 
        axis.text.y = element_text(face = "bold", size = 12, colour = "black"), 
        axis.title.y = element_text(face = "bold", size = 14, colour = "black"),
        axis.title.x = element_text(face = "bold", size = 14, colour = "black"),
        panel.background = element_blank(), 
        panel.border = element_rect(fill = NA, colour = "black"), 
        legend.key=element_blank()) + 
  labs(x = "MDS 1", y = "MDS 2", colour = "Cluster") 
# +
#   scale_fill_brewer(palette = "Paired", aesthetics = "colour")

```

```{r echo=FALSE, message=FALSE, warning=FALSE}

####
#graphs
####
grp <- grp %>%
  rownames_to_column(var = "docking_date_yy")

spp <- topspp%>%
  rownames_to_column(var = "id")%>%
  mutate(id = as.numeric(id))

landing%>%
  right_join(spp)%>%
  mutate(docking_date_yy = as.character(docking_date_yy)) %>% 
  right_join(grp)%>%
  group_by(grp, id, species_code)%>%
  summarise(nominal_mass = sum(nominal_mass, na.rm = T))%>%
  normalise(nominal_mass,grp, "grp")%>%
  mutate(norm = sqrt(norm))%>%
  ggplot(aes(reorder(species_code, id), norm))+ #, fill = grp
  geom_col(position = "dodge")+
  facet_wrap(~grp)+
  theme(
        axis.text.x = element_text(face = "bold",colour = "black", size = 8, 
                                   angle = 90, vjust = 0.5, hjust=1), 
        axis.text.y = element_text(face = "bold", size = 8, colour = "black"), 
        axis.title.y = element_text( face = "bold", size = 12, colour = "black"),
        axis.title.y.right = element_text( face = "bold", size = 12, colour = "blue"),
        axis.title.x = element_text(face = "bold", size = 12, colour = "black"),
        panel.background = element_blank(), 
        panel.border = element_rect(fill = NA, colour = "black")) +
  labs(x = "Species code", y = "Proportion")
# +
#   scale_fill_brewer(palette = "Paired", aesthetics = "fill")

 #       legend.key=element_blank()legend.title = element_blank(),legend.position = "none",
```
Simper analysis of year


```{r echo=FALSE, message=FALSE, warning=FALSE}


simp_year <- simper(year.s[2:14],year.s$grp)

comparisons <- c("Y4_Y3", "Y2_Y3", "Y2_Y4", "Y1_Y3", "Y1_Y2", "Y1_Y4")

simper.results <- c()

for(i in 1:length(comparisons)) {
require(tidyverse)
temp <- summary(simp_year)[as.character(comparisons[i])] %>%
as.data.frame()
colnames(temp) <- gsub(
paste(comparisons[i],".", sep = ""), "", colnames(temp))
temp <- temp %>%
mutate(Comparison = comparisons[i],
Position = row_number()) %>%
  rownames_to_column(var = "Species")
simper.results <- rbind(simper.results, temp)
}

simper.results.con <- simper.results %>%
  filter(p <= 0.05) %>%
  select(Species, average, Comparison) %>% 
  mutate(average = round(average*100, digits = 2)) %>% 
  pivot_wider(names_from = Comparison, values_from = average)


landing%>%
  right_join(spp)%>%
  mutate(docking_date_yy = as.character(docking_date_yy)) %>% 
  right_join(grp)%>%
  group_by(grp, id, species_code)%>%
  summarise(nominal_mass = round(mean(nominal_mass, na.rm = T), digits = 1)) %>% 
  pivot_wider(names_from = grp, values_from = nominal_mass) %>% 
  left_join(simper.results.con, by = c("species_code" = "Species"))%>% 
  ungroup() %>% 
  select(-id)%>%
  select(1,6:10) %>% 
  gt()

```

Cluster analysis of months
```{r echo=FALSE, message=FALSE, warning=FALSE}
####
#cluster
####

month<- landing %>%
  separate(land_id, c(NA,NA,NA,"docking_date"), sep = ",", remove = F )%>%
  mutate(docking_date = as.Date(docking_date)) %>%               
  mutate(month = months(docking_date)) %>% 
  mutate(season = quarter(docking_date)) %>% 
  mutate(season = if_else(season == 1, "Summer", 
                          if_else(season == 2, "Autumn", 
                                  if_else(season == 3, "Winter", "Spring"))))


test <- month%>%
  right_join(topspp)%>%
  group_by(month,season, species_code)%>%
  summarise(nominal_mass = sum(nominal_mass, na.rm = T))%>%
  normalise(nominal_mass, month, "month")%>%
  mutate(norm = sqrt(norm))%>%
  ungroup()%>%
  select(month, norm, species_code)%>%
  pivot_wider(names_from = species_code, values_from = norm)%>%
  mutate_all(~replace_na(.,0))%>%
  ungroup()%>%
  column_to_rownames(var = "month")

#write.csv(test, "simp.season.csv", row.names = F)

#distance matrix

dm <- vegdist(test, method="bray", na.rm = T)

#cluster

cluster<- dm %>%
  hclust(method = "average")

lbls <- c("1", "3", "2")

x <- cluster%>%
  as.dendrogram()%>% 
  dendextend::set("labels_cex", 0.8)%>%
  dendextend::set("branches_lwd", 2)%>%
  colour_branches(h = 0.06, groupLabels = lbls,
                  col = "black")

tdro3 <- reorder(x, c(1, 4, 8, 5, 9, 7, 2, 6, 3, 10, 11, 12), mean)
plot(tdro3)
title(ylab = 'Dissimilarity', line = 2.5)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# dend_list <- get_subdendrograms(x, 3)
# labels <- lapply(dend_list, labels)
# grp<- labels %>%
#   plyr::ldply( rbind)%>%
#   t()%>%
#   as_tibble()%>%
#   rename(S1 = V1,
#          S3 = V2,
#          S2 = V3)%>%
#   pivot_longer(cols= 1:3,names_to = "grp", values_drop_na = T )%>%
#   column_to_rownames(var = "value")
# 
# sea.s <- test %>% 
#   merge(grp, by = "row.names") %>% 
#   left_join(select(month, month, season), by = c("Row.names" = "month")) %>% 
#   distinct()
# #write.csv(sea.s, "simp.season.csv", row.names = F)
# 
# #### MDS
# 
# #distance matrix
# 
# dm <- vegdist(sea.s[2:14], method="bray", na.rm = T)
# 
# #Do MDS
# mds <- metaMDS(dm, 
#                k=3,
#                try=15, trymax=20,
#                autotransform = FALSE,#if it doesn't converge increase k by 1. 
#                trace = F)         
# 
# 
# MDS_xy <- data.frame(mds$points)
# 
# 
# ggplot(MDS_xy, aes(MDS1, MDS2,  shape = sea.s$season)) + #colour = sea.s$grp,
#   geom_point(size = 6) + 
#   ggforce::geom_mark_ellipse(aes(MDS1, MDS2, group = sea.s$grp, label = sea.s$grp))+
#   theme(legend.title = element_text(size = 14, face = "bold"), 
#         legend.text = element_text(size = 12, face = "bold"), 
#         legend.position = "right", 
#         axis.text.x = element_text(face = "bold",colour = "black", size = 12), 
#         axis.text.y = element_text(face = "bold", size = 12, colour = "black"), 
#         axis.title.y = element_text(face = "bold", size = 14, colour = "black"),
#         axis.title.x = element_text(face = "bold", size = 14, colour = "black"),
#         panel.background = element_blank(), 
#         panel.border = element_rect(fill = NA, colour = "black"), 
#         legend.key=element_blank()) + 
#   labs(x = "MDS 1", y = "MDS 2", colour = "group", shape = "season") +
#   scale_fill_brewer(palette = "Paired", aesthetics = "colour")

```

```{r echo=FALSE, message=FALSE, warning=FALSE}

####
#graphs
####

season<- grp %>%
  rownames_to_column(var = "month")
  

month%>%
  right_join(spp)%>%
  right_join(season)%>%
  group_by(grp, id, species_code)%>%
  summarise(nominal_mass = sum(nominal_mass, na.rm = T))%>%
  normalise(nominal_mass,grp, "grp")%>%
  mutate(norm = sqrt(norm))%>%
  ggplot(aes(reorder(species_code, id),  norm))+ #fill = grp,
  geom_col(position = "dodge")+
  ylim(0,NA)+
  facet_wrap(~grp)+
  theme(
        axis.text.x = element_text(face = "bold",colour = "black", size = 8, 
                                   angle = 90, vjust = 0.5, hjust=1), 
        axis.text.y = element_text(face = "bold", size = 8, colour = "black"), 
        axis.title.y = element_text( face = "bold", size = 12, colour = "black"),
        axis.title.y.right = element_text( face = "bold", size = 12, colour = "blue"),
        axis.title.x = element_text(face = "bold", size = 12, colour = "black"),
        panel.background = element_blank(), 
        panel.border = element_rect(fill = NA, colour = "black")) +
  labs(x = "Species code", y = "Proportion")
# +
#   scale_fill_brewer(palette = "Paired", aesthetics = "fill")

#legend.title = element_blank(), legend.key=element_blank()

```
Simper analysis of months


```{r echo=FALSE, message=FALSE, warning=FALSE}


simp_year <- simper(year.s[2:14],year.s$grp)

comparisons <- c("Y4_Y3", "Y2_Y3", "Y2_Y4", "Y1_Y3", "Y1_Y2", "Y1_Y4")

simper.results <- c()

for(i in 1:length(comparisons)) {
require(tidyverse)
temp <- summary(simp_year)[as.character(comparisons[i])] %>%
as.data.frame()
colnames(temp) <- gsub(
paste(comparisons[i],".", sep = ""), "", colnames(temp))
temp <- temp %>%
mutate(Comparison = comparisons[i],
Position = row_number()) %>%
  rownames_to_column(var = "Species")
simper.results <- rbind(simper.results, temp)
}

simper.results.con <- simper.results %>%
  filter(p <= 0.05) %>%
  select(Species, average, Comparison) %>% 
  mutate(average = round(average*100, digits = 2)) %>% 
  pivot_wider(names_from = Comparison, values_from = average)


landing%>%
  right_join(spp)%>%
  mutate(docking_date_yy = as.character(docking_date_yy))%>% 
  mutate(docking_date_mm = as.character(docking_date_mm))%>% 
  right_join(season, by = c("docking_date_mm" = "month"))%>%
  group_by(grp, id, species_code)%>%
  summarise(nominal_mass = round(mean(nominal_mass, na.rm = T), digits = 1)) %>% 
  pivot_wider(names_from = grp, values_from = nominal_mass) %>% 
  left_join(simper.results.con, by = c("species_code" = "Species"))%>% 
  ungroup() %>% 
  select(-id)%>%
  select(1,6:9) %>% 
  gt()

```
cluster analysis of area

```{r echo=FALSE, message=FALSE, warning=FALSE}
#area
#get world map
world <- getMap(resolution = "low")

#get country I want
RSA <- c("South Africa")

# Call the vector in `borders()`
world_saf <- world[world@data$ADMIN %in% RSA, ]

# comm_grids <- read.csv(here("data/ComGrids.csv")) %>% 
#   filter(inshore_area ==1)
# 
# grid_mid <- comm_grids%>%
#   mutate(mid_lat = (maximum_latitude+minimum_latitude)/2)%>%
#   mutate(mid_long = (maximum_longitude+minimum_longitude)/2)%>%
#   select(code, mid_lat, mid_long)%>%
#   mutate(grid_code = as.character(code), .keep = "unused")


#spp composition of area
#grid_code
####
#cluster
####

count <- drag %>%
  count(grid_code)%>%
  filter(!is.na(grid_code))%>%
  select(grid_code)

grid <- drag%>%
#  right_join(count)%>%
  right_join(topspp)%>%
  group_by(grid_code, species_code)%>%
  summarise(nominal_mass = sum(nominal_mass, na.rm = T))%>%
  normalise(nominal_mass, grid_code, "grid_code")%>%
  mutate(norm = sqrt(norm))%>%
  select(grid_code, norm, species_code)%>%
  pivot_wider(names_from = species_code, values_from = norm)%>%
  mutate_all(~replace_na(.,0))%>%
  ungroup()%>%
  column_to_rownames(var = "grid_code")

#write.csv(grid, "simp.area.csv", row.names = F)


#distance matrix

dm <- vegdist(grid, method="bray", na.rm = T)

#cluster

cluster<- dm %>%
  hclust(method = "average")

x <- cluster%>%
  as.dendrogram()%>% 
  dendextend::set("labels_cex", 0.7)%>%
  dendextend::set("branches_lwd", 2)%>%
  colour_branches(h = 0.13, groupLabels = TRUE,
                  col = "black")
plot(x)
title(ylab = 'Dissimilarity', line = 2.5)
title(xlab = 'Grid cells', line = 2)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}

# dend_list <- get_subdendrograms(x,10)
# labels <- lapply(dend_list, labels)
# grp<- labels %>%
#   plyr::ldply( rbind)%>%
#   t()%>%
#   as_tibble()%>%
#   rename(G1 = V1,
#          G2 = V2,
#          G3 = V3,
#          G4 = V4,
#          G5 = V5,
#          G6 = V6,
#          G7 = V7,
#          G8 = V8,
#          G9 = V9,
#          G10 = V10)%>%
#   pivot_longer(cols= 1:10,names_to = "grp", values_drop_na = T )%>%
#   column_to_rownames(var = "value")
# 
# 
# 
# grid.s <- grid %>%
#   merge( grp, by="row.names") %>%
#   mutate(grp = if_else(grp == "G2", "G3", grp))%>%
#   mutate(grp = if_else(grp == "G4", "G5", grp))%>%
#   mutate(grp = if_else(grp == "G7", "G8", grp))
# 
# #write.csv(grid.s, "simp.area.csv", row.names = F)
# #### MDS
# 
# #distance matrix
# 
# 
# dm <- vegdist(grid.s[2:14], method="bray", na.rm = T)
# 
# #Do MDS
# mds <- metaMDS(dm, 
#                k=3,
#                try=15, trymax=20,
#                autotransform = FALSE,
#                trace = F)         #if it doesn't converge increase k by 1. 
# 
# 
# MDS_xy <- data.frame(mds$points)
# 
# 
# ggplot(MDS_xy, aes(MDS1, MDS2 )) +   #, shape =grid.s$grp
#   geom_point(size = 6)+
#   ggforce::geom_mark_ellipse(aes(MDS1, MDS2, group = grid.s$grp))+
#   #  geom_text(label = grid.s$Row.names)+
#   theme(legend.title = element_text(size = 14, face = "bold"), 
#         legend.text = element_text(size = 12, face = "bold"), 
#         legend.position = "right", 
#         axis.text.x = element_text(face = "bold",colour = "black", size = 12), 
#         axis.text.y = element_text(face = "bold", size = 12, colour = "black"), 
#         axis.title.y = element_text(face = "bold", size = 14, colour = "black"),
#         axis.title.x = element_text(face = "bold", size = 14, colour = "black"),
#         panel.background = element_blank(), 
#         panel.border = element_rect(fill = NA, colour = "black"), 
#         legend.key=element_blank()) + 
#   labs(x = "MDS 1", y = "MDS 2", colour = "group", shape = "group") +
#   scale_fill_brewer(palette = "Paired", aesthetics = "colour", 
#                     breaks=c('G1', 'G2','G3','G4','G5',
#                              'G6', 'G7', 'G8', 'G9', 'G10'))
# 

```

```{r echo=FALSE, message=FALSE, warning=FALSE}

#map
#grids.map <- read.csv(here("data/map_grid.csv"))
test <- grid.s %>% 
  count(Row.names)

test <- drag %>% 
  count(grid_code)

grid.s <- grid.s %>%
  mutate(Row.names = as.numeric(Row.names)) %>% 
  left_join(distinct(select(drag, grid_code, mid_lat, mid_long)), by = c("Row.names"="grid_code"))%>%
  select(c(Row.names, grp, mid_lat, mid_long))

ggplot() +
  geom_polygon(data = world_saf, 
               aes(x=long, y=lat, group=group), 
               fill="grey", 
               colour="black") +
  coord_quickmap() +
  coord_sf(xlim = c(18.00, 28.00), ylim = c(-32.00, -37.00), expand = T) +
  #   geom_segment(data = grids.map, aes(x = vlong_start, 
  #                                      y= vlat_start, 
  #                                      xend = vlong_end,
  #                                      yend = vlat_end) )+
  #   geom_segment(data = grids.map, aes(x = hlong_start, 
  #                                      y= hlat_start, 
  #                                      xend = hlong_end,
  #                                      yend = hlat_end) ) +
  geom_point(data=grid.s, aes(mid_long, mid_lat,  alpha=I(0.7), colour = grp),
             size = 6, shape = 15) +
  labs(x="", y="", colour = "Groups") +
  scale_fill_brewer(palette = "Paired", aesthetics = "colour", 
                    breaks=c('G1', 'G2','G3','G4','G5',
                             'G6','G7','G8','G9','G10',
                             'G11','G12'))+
  theme_bw()

#  north(world_saf, location = "topmright", symbol = 15) +
#  scale_fill_continuous(low = "#fff7ec", high = "#7F0000")+
#  scalebar(world_saf, dist = 4, dist_unit = "m",
#           transform = FALSE, model = "WGS84") +
#  blank() +
#  scale_fill_continuous(low = "#fff7ec", high = "#7F0000")

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
spp <- topspp %>%
  rownames_to_column(var = "id")%>%
  mutate(id = as.numeric(id))

grp.1 <- grp %>%
  rownames_to_column(var = "grid_code")

test <- drag%>%
  mutate(grid_code = as.character(grid_code)) %>% 
  right_join(spp) %>%
  right_join(grp.1) %>%
  group_by(grp, id, species_code) %>%
  summarise(nominal_mass = sum(nominal_mass, na.rm = T)) %>%
  normalise(nominal_mass,grp, "grp") %>%
  mutate(norm = sqrt(norm))%>%
  mutate(grp = if_else(grp == "G2", "G3", grp))%>%
  mutate(grp = if_else(grp == "G4", "G5", grp))%>%
  mutate(grp = if_else(grp == "G7", "G8", grp))

test%>%
  ggplot(aes(reorder(species_code, id), norm))+
  geom_col(position = "dodge")+
  facet_wrap(~grp, scales = "free_y")+
  theme(
        axis.text.x = element_text(face = "bold",colour = "black", size = 8,
                                   angle = 90, vjust = 0.5, hjust=1), 
        axis.text.y = element_text(face = "bold", size = 8, colour = "black"), 
        axis.title.y = element_text( face = "bold", size = 12, colour = "black"),
        axis.title.y.right = element_text( face = "bold", size = 12, colour = "blue"),
        axis.title.x = element_text(face = "bold", size = 12, colour = "black"),
        panel.background = element_blank(), 
        panel.border = element_rect(fill = NA, colour = "black")) +
  labs(x = "Species", y = "Proportion")
# +
#   scale_fill_brewer(palette = "Paired", aesthetics = "fill")

# legend.title = element_blank(), 
#         legend.text = element_blank(), 
#         legend.position = "none", 
#         legend.key=element_blank()

```

differences in vessel catches by area across the months
```{r echo=FALSE, message=FALSE, warning=FALSE}
##are vessels fishing in the same blocks the whole year? 
##if not, are all vessels fishing in the same areas?

##get each vessels effort per grid cell per month

seasonal_effort_per_ves <- drag %>% 
  distinct(drag_id, vessel_number, docking_date_mm, grid_code) %>% 
  count(vessel_number, docking_date_mm, grid_code) %>%  #count number of trawls in each grid, each month, per vessel
  unite(col = "id",  vessel_number, docking_date_mm, sep = "_", remove = F) %>% 
  normalise(n, id, "id") %>% 
  mutate(norm = sqrt(norm))%>%
  select(vessel_number, docking_date_mm, grid_code, norm) %>% 
  pivot_wider(names_from = grid_code, values_from = norm) %>%
  mutate_all(~replace_na(.,0)) %>%
  left_join(select(ves.s, Row.names, grp, target_code), by = c("vessel_number" = "Row.names"))%>% 
  mutate(vessel_number = as.character(vessel_number)) %>% 
  mutate(season = quarter(docking_date_mm)) %>% 
  mutate(season = if_else(season == 1, "Summer", 
                          if_else(season == 2, "Autumn", 
                                  if_else(season == 3, "Winter", "Spring")))) %>% 
  mutate(docking_date_mm = as.character(docking_date_mm))



dm <- vegdist(seasonal_effort_per_ves[3:56], method="bray", na.rm = T)

#Do MDS
mds <- metaMDS(dm, 
               k=3,
               try=15, trymax=20,
               autotransform = FALSE,
               trace = F)         #if it doesn't converge increase k by 1. 


MDS_xy <- data.frame(mds$points)


ggplot(MDS_xy, aes(MDS1, MDS2)) +   
  geom_point(aes(shape = seasonal_effort_per_ves$grp,
                   fill = seasonal_effort_per_ves$season) ,
             size = 4)+
#  ggforce::geom_mark_ellipse(aes(MDS1, MDS2, group = seasonal_effort_per_ves$grp, label= seasonal_effort_per_ves$grp))+
  #  geom_text(label = grid.s$Row.names)+
  theme(legend.title = element_text(size = 14, face = "bold"), 
        legend.text = element_text(size = 12, face = "bold"), 
        legend.position = "right", 
        axis.text.x = element_text(face = "bold",colour = "black", size = 12), 
        axis.text.y = element_text(face = "bold", size = 12, colour = "black"), 
        axis.title.y = element_text(face = "bold", size = 14, colour = "black"),
        axis.title.x = element_text(face = "bold", size = 14, colour = "black"),
        panel.background = element_blank(), 
        panel.border = element_rect(fill = NA, colour = "black"), 
        legend.key=element_blank()) + 
  labs(x = "MDS 1", y = "MDS 2", fill = "Season", shape = "species group") +
  scale_fill_brewer(palette = "Paired", aesthetics = "fill")+
  scale_shape_manual(values = c( 25,22,  24, 21, 23)) +
  guides(fill = guide_legend("Season", override.aes = list(shape = 21)))

ggsave("outputs/vessel_area_month.png", width = 40, height = 30, units = "cm")

# shape = seasonal_effort_per_ves$target_code,
```



```{r echo=FALSE, message=FALSE, warning=FALSE}
##do permanova
permanova <- adonis2(dm~ vessel_number+docking_date_mm, data = seasonal_effort_per_ves[1:2], by =   "terms")
permanova%>% 
  rownames_to_column(var = "ExplanatoryVariables") %>% 
  gt()



```



Catch composition model per trip
```{r echo=FALSE, message=FALSE, warning=FALSE}
#permanova model 1
## PERMANOVA model 1 - year, season, vessel - trip data

test <- landing%>%
  right_join(topspp)%>%
  select(-scientific_name) %>% 
#  mutate(cpue = nominal_mass/trip_length_dd) %>% 
  normalise(nominal_mass, land_id, "land_id")%>%
  mutate(norm = sqrt(norm))%>%
  select(-c(nominal_mass)) %>% 
  distinct() %>% 
  pivot_wider(names_from = species_code, values_from = norm)%>%
  mutate_all(~replace_na(.,0)) %>% 
  mutate(docking_date_yy = as.character(docking_date_yy))%>% 
  mutate(docking_date_mm = as.character(docking_date_mm))%>% 
  mutate(vessel_number = as.character(vessel_number))



#random sample
test.1 <- test %>%
  slice_sample(prop = 0.01)

#distance matrix

dm <- vegdist(test.1[7:19], method="bray", na.rm = T)


#Do a PERMANOVA

permanova <- adonis2(dm~ docking_date_yy+docking_date_mm+vessel_number, data = test.1[1:6], by = "terms")
permanova%>% 
  rownames_to_column(var = "ExplanatoryVariables") %>% 
  gt()

```

ANOVA's of the variable's dispersions

```{r echo=FALSE, message=FALSE, warning=FALSE}

# do dispersion test to see if centroids or dispersions differ 
year <- betadisper(dm, test.1$docking_date_yy, type = "centroid")

vessel <- betadisper(dm, test.1$vessel_number, type = "centroid")

month <- betadisper(dm, test.1$docking_date_mm, type = "centroid")


# do anova of dispersions
anova.year<- anova(year)
anova.year%>% 
  rownames_to_column(var = "Year") %>% 
  gt()

anova.ves <-  anova(vessel)
anova.ves%>% 
  rownames_to_column(var = "Vessel") %>% 
  gt()

anova.sea <- anova(month)
anova.sea%>% 
  rownames_to_column(var = "Month") %>% 
  gt()

# plot the dispersions

plot(year, hull=FALSE, ellipse=TRUE)
plot(vessel, hull=FALSE, ellipse=TRUE)
plot(month, hull=FALSE, ellipse=TRUE)


```

Catch composition model per trawl

```{r echo=FALSE, message=FALSE, warning=FALSE}
## area permanova - trawl data

###make data

# drag.effort <- drags.1%>%
#   mutate(trawl_length_hh = if_else(!between(trawl_length_hh, 0.5, 9),
#                                    3.5, trawl_length_hh))%>%
#   group_by(drag_id)%>%
#   summarise(trawl_length_hh = sum(trawl_length_hh, na.rm = T))

area <- drag %>%
  filter(vessel_number %in% c('96', '93', '191', '244', "225"))%>%
  filter(grid_code %in% c('512', '525','524', '514', '513', '523', '526', '554', '540', '555'))%>%
  filter(docking_date_yy %in% c('2004', '2006'))




## PERMANOVA

test <- area%>%
  filter(nominal_mass != 0)%>%
  right_join(topspp)%>%
  select(-scientific_name) %>% 
  normalise(nominal_mass, drag_id, "drag_id")%>%
  mutate(norm = sqrt(norm))%>%
  select(-c(nominal_mass))%>%
  pivot_wider(names_from = species_code, values_from = norm)%>%
  mutate_all(~replace_na(.,0)) %>% 
  mutate(docking_date_yy = as.character(docking_date_yy))%>% 
  mutate(docking_date_mm = as.character(docking_date_mm))%>% 
  mutate(vessel_number = as.character(vessel_number))%>% 
  mutate(grid_code = as.character(grid_code))



#random sample
test.1 <- test %>%
  slice_sample(prop = 0.01)

spp <- test.1 %>%
  select(-c(land_id, drag_id,  docking_date_yy, docking_date_mm,
            vessel_number, grid_code, target_species_code, 
            trawl_length_hh))

env <- test.1 %>%
  select(c(land_id, drag_id,  docking_date_yy, docking_date_mm,
            vessel_number, grid_code, target_species_code, 
            trawl_length_hh))


write.csv(spp, "area.cluster.spp.csv", row.names = F)
write.csv(env, "area.cluster.env.csv", row.names = F)

#distance matrix

dm <- vegdist(test.1[10:22], method="bray", na.rm = T)


#Do a PERMANOVA

permanova2 <- adonis2(dm~ docking_date_yy+docking_date_mm+grid_code+vessel_number, data = test.1[3:6], by = "terms")
permanova2%>% 
  rownames_to_column(var = "ExplanatoryVariables") %>% 
  gt()

```

ANOVA's of the variable's dispersions
```{r echo=FALSE, message=FALSE, warning=FALSE}

# do dispersion test to see if centroids or dispersions differ 
year <- betadisper(dm, test.1$docking_date_yy, type = "centroid")

vessel <- betadisper(dm, test.1$vessel_number, type = "centroid")

grid <- betadisper(dm, test.1$grid_code, type = "centroid")


# do anova of dispersions
anova.year<- anova(year)
anova.year%>% 
  rownames_to_column(var = "Year") %>% 
  gt()

anova.ves <-  anova(vessel)
anova.ves%>% 
  rownames_to_column(var = "Vessel") %>% 
  gt()

anova.grid <- anova(grid)
anova.grid%>% 
  rownames_to_column(var = "Grid code") %>% 
  gt()

# plot the dispersions

plot(year, hull=FALSE, ellipse=TRUE)
plot(vessel, hull=FALSE, ellipse=TRUE)
plot(grid, hull=FALSE, ellipse=TRUE)


```


```{r echo=FALSE, message=FALSE, warning=FALSE}
# 
# test <- dit_landings %>% 
#   filter(docking_date_yy == 2019) %>% 
#   distinct(vessel_number)
# 
# test <- landings.1  %>% 
#   summarise(mean = mean(trip_length_dd))
# 
# test <- landings.1  %>% 
#   summarise(mean = mean(number_of_drags))
# 


```


