---
title: "Clean data"
author: "Natasha Besseling"
date: "2023-04-28"
output: html_document
---

load packages

```{r}
library(janitor)
library(tidyverse)
library(lubridate)
library(here)
```


load data

```{r}
drag.catches <- read.csv(here("data/drag.catches.csv"))
drags <- read.csv(here("data/drags.csv"))
drags.no.effort <- read.csv(here("data/drags.no.effort.csv"))
landings <- read.csv(here("data/landings.csv"))
landings.catches <- read.csv(here("data/landings.catches.csv"))
convert <- read.csv(here("data/convert.csv"))

```



Load functions

```{r}
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

## get decade from year
floor_decade    = function(value){ return(value - value %% 10) }

## Normalise data
normalise <- function(dat, values, id, join) {
  
  test <- dat %>%
    group_by({{id}}) %>%
    summarise(total = sum({{values}}))
  
  test1 <-  dat %>%
    left_join(test, by = {{join}})
  
  test2 <- test1 %>%
    mutate(norm = {{values}} /total)%>%
    select(-total)
}
```


Filter out only fields I need for this project

```{r}
drag.catches <- drag.catches %>% 
  select(drag_ID, docking_date_yy, species_code, category_code, cleaned_mass, nominal_mass)

drags <- drags %>% 
  select(-c(country_code, company_number, permit_holder, permit_holder_user_id, product_list_code, true_course, magnetic_course, bottom_temperature, surface_temperature, wind_direction, wind_force, gear_type_code, rpm, pitch, catch_volume, catch_production, validated, validate_user_id))

drags.no.effort <- drags.no.effort %>% 
  select(land_id, drag_noeffort_ID, species_code, category_code, nominal_mass)

landings <- landings %>% 
  select(land_ID, vessel_number, docking_date_yy, docking_date_mm, docking_date_dd, docking_date_hh, docking_date_mi, sailing_date_yy, sailing_date_mm, sailing_date_dd, sailing_date_hh, sailing_date_hh, sailing_date_mi, bottom_trawl, midwater_trawl, freezer_landing, wetfish_landing, number_of_drags)

landings.catches <- landings.catches %>% 
  select(land_ID, species_code, category_code, landed_mass)
  
  
```


Filter data to only trawls in the inshore grids 
Make sure to only keep trips where all trawls occur inside the inshore trawl grounds

define inshore grids (is_grds)

```{r}
is_grds <- c('512',
'513',
'514',
'515',
'516',
'517',
'518',
'519',
'520',
'521',
'522',
'523',
'524',
'525',
'526',
'527',
'530',
'531',
'532',
'533',
'535',
'536',
'537',
'538',
'539',
'540',
'541',
'550',
'551',
'622',
'625',
'628',
'629',
'632',
'633',
'636',
'637',
'640'
)
```


filter records using these grids

```{r}
#only keep trawls outside inshore grids
only_isgrds <- drags %>%
  mutate(grid_code = as.character(grid_code)) %>% 
  filter( !grid_code %in% is_grds)%>%
  distinct(land_ID)

#delete all trips that contain at least one of these trawls

landings <- landings %>% 
  anti_join(only_isgrds)

#now only keep trawls from these trips

drags <- drags %>% 
  semi_join(landings, by = "land_ID")

#now only keep the catch records from these trips and trawls

landings.catches <- landings.catches %>%
  semi_join(landings, by = "land_ID")

drag.catches <- drag.catches %>% 
  semi_join(drags, by = "drag_ID")

drags.no.effort <- drags.no.effort %>% 
  semi_join(landings, by = c("land_id" = "land_ID"))
  

```


only keep trips that only trageted either hake or sole
define target species (is_trgt)

```{r}
is_trgt <- c("HAKE", "ECSOlE", "SOLE"
)
```


filter records using these targets

```{r}
#only keep trawls that don't target hake or sole
only_istrgt <- drags %>%
  filter(!target_species_code %in% is_trgt) %>%
  distinct(land_ID)

#delete all trips that contain at least one of these trawls

landings <- landings %>% 
  anti_join(only_istrgt)

#now only keep trawls from these trips

drags <- drags %>% 
  semi_join(landings, by = "land_ID")

#now only keep the catch records from these trips and trawls

landings.catches <- landings.catches %>%
  semi_join(landings, by = "land_ID")

drag.catches <- drag.catches %>% 
  semi_join(drags, by = "drag_ID")

drags.no.effort <- drags.no.effort %>% 
  semi_join(landings, by = c("land_id" = "land_ID"))


```

save data

```{r}
write.csv(drag.catches, file = here("outputs/drag.catches.1.csv"), row.names = F)
write.csv(drags, file = here("outputs/drags.1.csv"), row.names = F)
write.csv(drags.no.effort, file = here("outputs/drags.no.effort.1.csv"), row.names = F)
write.csv(landings, file = here("outputs/landings.1.csv"), row.names = F)
write.csv(landings.catches, file = here("outputs/landings.catches.1.csv"), row.names = F)
write.csv(convert, file = here("outputs/convert.1.csv"), row.names = F)
```









